Gafo-cc-analysis

### 2023-12-11 analysis/gafo-cc-analysis.Rmd
prep model runs

```{r}
scdata <- mdata%>%
  filter(touchscreen != 2
         )%>%
  group_by(subjid, community, ageinyears, touchscreen, household, children, younger_children)%>%
  summarise(mean_click = mean(click))%>%
  mutate(older_children = children - 1 - younger_children)%>%
  group_by(community)%>%
  mutate(
         household = scale(household), 
         children = scale(children), 
         older_children = scale(older_children),
         younger_children = scale(younger_children)

@@

```{r}
bm_base <- brm(mean_click ~ ageinyears + (ageinyears |community), 
                              data   = scdata, 
                              family = lognormal(),
                              warmup = 2000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4,
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")%>%
  add_criterion(., c("waic","loo"))

@@

bm_fullc_fix <- brm(mean_click ~ ageinyears + touchscreen + younger_children + older_children + (ageinyears |community), 
                              data   = scdata, 
                              family = lognormal(),
                              warmup = 2000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4,
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")%>%
  add_criterion(., c("waic","loo"))

bm_full_rand <- brm(mean_click ~ ageinyears + touchscreen + household + younger_children + children + (touchscreen + household + younger_children + children + ageinyears |community), 
                              data   = scdata, 
                              family = lognormal(),
                              warmup = 2000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4,
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")%>%
  add_criterion(., c("waic","loo"))

@@

bm_cts_rand <- brm(mean_click ~ ageinyears + children + touchscreen + (ageinyears + children + touchscreen |community), 
                              data   = scdata, 
                              family = lognormal(),
                              warmup = 2000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4,
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")%>%
  add_criterion(., c("waic","loo"))

@@

bm_ycts_fix <- brm(mean_click ~ ageinyears + touchscreen + younger_children + (ageinyears |community), 
                              data   = scdata, 
                              family = lognormal(),
                              warmup = 2000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4,
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")%>%
  add_criterion(., c("waic","loo"))

bm_octs_fix <- brm(mean_click ~ ageinyears + touchscreen + older_children + (ageinyears |community), 
                              data   = scdata, 
                              family = lognormal(),
                              warmup = 2000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4,
             control = list(adapt_delta = 0.95),
             backend = "cmdstanr")%>%
  add_criterion(., c("waic","loo"))
```

```{r}
loo_compare(bm_base,
            bm_full_fix, 
            bm_full_rand,
            bm_fullc_fix,
            bm_cts_fix,
            bm_ycts_fix,
            bm_octs_fix
            #bm_hhts_fix#,
            #bm_cts_fix_int,
            #bm_cts_rand_int,
            #bm_cts_rand#,
            #bm_hhts_rand_2, 
            #bm_hhts_rand
            )%>%as_tibble(rownames = "model")

model_weights(bm_base, 
            bm_octs_fix, criterion = "loo")%>%as_tibble(rownames = "model")

fixef(bm_octs_fix)
```
```{r}
ndata <- scdata%>%
  distinct(community, ageinyears)

@@

ggplot()+
  geom_smooth(data = post, aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
  theme_bw()+
  scale_color_ptol(name = "Community")+
  scale_fill_ptol(name = "Community")+
  labs(x = "Age", y="Imprecision")#+
  facet_wrap(~community)+guides(col = "none", fill = "none")
```

@@

```{r}
ncdata <- scdata%>%
  distinct(community)%>%
  expand_grid(ageinyears = 0)%>%
  mutate(touchscreen = 1)%>%
  expand_grid(children = c(min(scdata$children):max(scdata$children)))

cpost <- fitted(bm_cts_rand_int, newdata = ncdata, re_formula =~(children|community))%>%
  as_tibble() %>%
  bind_cols(ncdata)

ggplot()+
  geom_smooth(data = cpost, aes(x = children, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
  theme_bw()+
  scale_color_ptol(name = "Community")+
  scale_fill_ptol(name = "Community")+
  facet_grid(~community)+
  labs(x = "No of children (scaled)", y="Imprecision")

@@

>>>>

```{r}
scdata <- mdata%>%
  filter(touchscreen != 2
         )%>%
  group_by(subjid, community, ageinyears, touchscreen, household, children, younger_children)%>%
  summarise(mean_click = mean(click))%>%
  mutate(older_children = children - 1 - younger_children)%>%
  ungroup()%>%
  group_by(community)%>%
  mutate(
         household = scale(household), 
         children = scale(children), 
         older_children = scale(older_children),
         younger_children = scale(younger_children)

@@

```{r}
bm_base <- brm(mean_click ~ ageinyears + (ageinyears |community), 
                              data   = scdata, 
                              family = lognormal(),
                              warmup = 2000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4,
             control = list(adapt_delta = 0.95),
             #backend = "cmdstanr"
             )%>%
  add_criterion(., c("waic","loo"))

@@

bm_fullc_fix <- brm(mean_click ~ ageinyears + touchscreen + younger_children + older_children + (ageinyears |community), 
                              data   = scdata, 
                              family = lognormal(),
                              warmup = 2000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4,
             control = list(adapt_delta = 0.95),
             #backend = "cmdstanr"
             )%>%
  add_criterion(., c("waic","loo"))

bm_full_rand <- brm(mean_click ~ ageinyears + touchscreen + household + younger_children + older_children + (touchscreen + household + younger_children + older_children + ageinyears |community), 
                              data   = scdata, 
                              family = lognormal(),
                              warmup = 2000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4,
             control = list(adapt_delta = 0.95),
             #backend = "cmdstanr"
             )%>%
  add_criterion(., c("waic","loo"))

@@

bm_cts_rand <- brm(mean_click ~ ageinyears + children + touchscreen + (ageinyears + children + touchscreen |community), 
                              data   = scdata, 
                              family = lognormal(),
                              warmup = 2000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4,
             control = list(adapt_delta = 0.95),
             #backend = "cmdstanr"
             )%>%
  add_criterion(., c("waic","loo"))

@@

bm_ycts_fix <- brm(mean_click ~ ageinyears + touchscreen + younger_children + (ageinyears |community), 
                              data   = scdata, 
                              family = lognormal(),
                              warmup = 2000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4,
             control = list(adapt_delta = 0.95),
             #backend = "cmdstanr"
             )%>%
  add_criterion(., c("waic","loo"))

bm_octs_fix <- brm(mean_click ~ ageinyears + touchscreen + older_children + (ageinyears |community), 
                              data   = scdata, 
                              family = lognormal(),
                              warmup = 2000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4,
             control = list(adapt_delta = 0.95),
            # backend = "cmdstanr"
             )%>%
  add_criterion(., c("waic","loo"))

bm_octs_fix_int <- brm(mean_click ~  touchscreen + ageinyears * older_children + (ageinyears |community), 
                              data   = scdata, 
                              family = lognormal(),
                              warmup = 2000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4,
             control = list(adapt_delta = 0.95),
            # backend = "cmdstanr"
             )%>%
  add_criterion(., c("waic","loo"))

bm_octs_rand <- brm(mean_click ~ ageinyears + touchscreen + older_children + (ageinyears + older_children |community), 
                              data   = scdata, 
                              family = lognormal(),
                              warmup = 2000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4,
             control = list(adapt_delta = 0.95),
             #backend = "cmdstanr"
             )%>%
  add_criterion(., c("waic","loo"))

bm_octs_rand_int <- brm(mean_click ~ touchscreen + ageinyears*older_children + (ageinyears * older_children |community), 
                              data   = scdata, 
                              family = lognormal(),
                              warmup = 2000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4,
             control = list(adapt_delta = 0.95),
             #backend = "cmdstanr"
             )%>%
  add_criterion(., c("waic","loo"))
```

```{r}
loo_compare(bm_base,
            #bm_full_fix, 
            bm_full_rand,
            bm_fullc_fix,
            #bm_cts_fix,
            #bm_ycts_fix,
            bm_octs_fix,
            bm_octs_fix_int,
            bm_octs_rand_int,
            bm_octs_rand#,
            #bm_full_rand
            #bm_hhts_fix#,
            #bm_cts_fix_int,
            #bm_cts_rand_int,
            #bm_cts_rand#,
            #bm_hhts_rand_2, 
            #bm_hhts_rand
            )%>%as_tibble(rownames = "model")

model_weights(bm_base,
            #bm_full_fix, 
            bm_full_rand,
            bm_fullc_fix,
            #bm_cts_fix,
            #bm_ycts_fix,
            bm_octs_fix,
            bm_octs_fix_int,
            bm_octs_rand_int,
            bm_octs_rand,
            #bm_full_rand
            #bm_hhts_fix#,
            #bm_cts_fix_int,
            #bm_cts_rand_int,
            #bm_cts_rand#,
            #bm_hhts_rand_2, 
            #bm_hhts_rand,
            criterion = "loo")%>%as_tibble(rownames = "model")

fixef(bm_cts_rand)
```
```{r}
ndata <- scdata%>%
  distinct(community, ageinyears)

@@

ggplot()+
  geom_smooth(data = post, aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
  theme_bw()+
  scale_color_manual(name = "Community", values = colors)+
  scale_fill_manual(name = "Community", values = colors)+
  labs(x = "Age", y="Imprecision")#+
  facet_wrap(~community)+guides(col = "none", fill = "none")
```

@@

```{r}
ncdata <- scdata%>%
  distinct(community)%>%
  expand_grid(ageinyears = 0)%>%
  mutate(touchscreen = 1)%>%
  expand_grid(older_children = c(min(scdata$older_children):max(scdata$older_children)))

cpost <- fitted(bm_octs_rand, newdata = ncdata, re_formula =~(older_children|community))%>%
  as_tibble() %>%
  bind_cols(ncdata)

ggplot()+
  geom_smooth(data = cpost, aes(x = older_children, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
  theme_bw()+
  scale_color_manual(name = "Community", values = colors)+
  scale_fill_manual(name = "Community", values = colors)+
  facet_wrap(~community, nrow = 2)+
  labs(x = "No of children older than the target child (scaled)", y="Imprecision")

@@

```{r}
ncdata <- scdata%>%
  distinct(community)%>%
  expand_grid(ageinyears = c(-1, 0, 1))%>%
  mutate(touchscreen = 1)%>%
  expand_grid(older_children = c(min(scdata$older_children):max(scdata$older_children)))

cpost <- fitted(bm_octs_rand_int, newdata = ncdata, re_formula =~(older_children|community))%>%
  as_tibble() %>%
  bind_cols(ncdata)

ggplot()+
  geom_smooth(data = cpost, aes(x = older_children, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill = factor(ageinyears), col = factor(ageinyears)), stat = "identity", alpha = .25)+
  theme_bw()+
  scale_color_ptol()+
  scale_fill_ptol()+
  facet_wrap(~community, nrow = 2)+
  labs(x = "No of children older than the target child (scaled)", y="Imprecision")

```{r}
ggsave("../visuals/old_child_site.png", width = 12, height = , bg = "white")
```
